Cartograms with Dynamic Features

### 2022-05-30 paper/section/main.tex
draft: update flowchart

 {
  \begin{figure}[tb!]
      \centering
      \includegraphics[width=\columnwidth]{example-image-a}
      \caption{An screenshot of \software. Figure TBA.}
      \label{fig:overview}
  \end{figure}
 }

 {
  \begin{figure}[tb!]
      \centering
      \includegraphics[width=0.8\columnwidth]{figure/flowchart.png}
      \caption{A flowchart illustration of our layout algorithm.See \figref{fig:flowchart-stalemate} for the flow of processing stalemate. See also \algoref{alg:UpdateNodePosition} for more detail.}
      \label{fig:flowchart}
  \end{figure}

  \begin{figure}[tb!]
      \centering
      \includegraphics[width=0.9\columnwidth]{figure/flowchart stalemate.png}
      \caption{A flowchart illustration of stalemate processing.}
      \label{fig:flowchart-stalemate}
  \end{figure}
 }

\algoref{alg:UpdateNodePosition} and \figref{fig:flowchart} provide an overview of the process.

@@

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth]{figure/river_resolution.png}
            \caption{The resolution of rivers can be dynamically adjusted by the user. A shows River Thames at its original resolution with 10,170 edges. B shows the river at a reduced resolution of 49 edges. We further smooth the river by removing vertices in dense areas, as shown in C. The reduced resolution preserves the majority of River Thames' original shape and improves the performance of our river intersection tests.}
            \label{fig:river resolution}
        \end{figure}
    }

@@

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth]{figure/stalemate.png}
            \caption{A stalemate situation is when a node's translation path $ \nodeVectorCT $ (in iteration 1) intersects a river $ \stalemateMax $ times. The node is translated back to its previous position (iteration 2). A stalemate often occurs when the area is congested and the node is unable to translate to a new position without intersecting a river.}
            \label{fig:stalemate}
        \end{figure}
    }

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth]{figure/corridor.png}
            \caption{A stalemate occurs when a node's translation path $ \nodeVectorCT $ intersects a river for $ \stalemateMax $ times, as shown in A. To address the issue, we derive a corridor (orange rectangle in E) based on $ \node $ and $ \nodeFNOR $. All nodes within the corridor are translated based on $ \nodeVectorTC $, such that $ \nodeVectorNNn = \nodeVectorNinNinn $. In order to show a clear illustration, we place nodes sparsely in this figure.}
            \label{fig:corridor}
        \end{figure}
    }

>>>>

 {
  \begin{figure}[tb!]
      \centering
      \includegraphics[width=\columnwidth,keepaspectratio]{example-image-a}
      \caption{An screenshot of \software. Figure TBA.}
      \label{fig:overview}
  \end{figure}
 }

 {
  \begin{figure*}[tb!]
      \centering
      \includegraphics[width=\textwidth,height=0.95\textheight,keepaspectratio]{figure/flowchart.png}
      \caption{A flowchart illustration of our layout algorithm.See \figref{fig:flowchart-stalemate} for the flow of processing stalemate. See also \algoref{alg:UpdateLayout} for more detail.}
      \label{fig:flowchart}
  \end{figure*}

  \begin{figure}[tb!]
      \centering
      \includegraphics[width=0.9\columnwidth,keepaspectratio]{figure/flowchart stalemate.png}
      \caption{A flowchart illustration of stalemate processing.}
      \label{fig:flowchart-stalemate}
  \end{figure}
 }

\algoref{alg:UpdateLayout} and \figref{fig:flowchart} provide an overview of the process.

@@

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/river_resolution.png}
            \caption{The resolution of rivers can be dynamically adjusted by the user. A shows River Thames at its original resolution with 10,170 edges. B shows the river at a reduced resolution of 49 edges. We further smooth the river by removing vertices in dense areas, as shown in C. The reduced resolution preserves the majority of River Thames' original shape and improves the performance of our river intersection tests.}
            \label{fig:river resolution}
        \end{figure}
    }

@@

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/stalemate.png}
            \caption{A stalemate situation is when a node's translation path $ \nodeVectorCT $ (in iteration 1) intersects a river $ \stalemateMax $ times. The node is translated back to its previous position (iteration 2). A stalemate often occurs when the area is congested and the node is unable to translate to a new position without intersecting a river.}
            \label{fig:stalemate}
        \end{figure}
    }

    {
        \begin{figure}[tb!]
            \centering
            \includegraphics[width=\columnwidth,keepaspectratio]{figure/corridor.png}
            \caption{A stalemate occurs when a node's translation path $ \nodeVectorCT $ intersects a river for $ \stalemateMax $ times, as shown in A. To address the issue, we derive a corridor (orange rectangle in E) based on $ \node $ and $ \nodeFNOR $. All nodes within the corridor are translated based on $ \nodeVectorTC $, such that $ \nodeVectorNNn = \nodeVectorNinNinn $. In order to show a clear illustration, we place nodes sparsely in this figure.}
            \label{fig:corridor}
        \end{figure}
    }
